---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# snippet

<!-- badges: start -->
<!-- badges: end -->

`snippet` creates shareable, syntax-highlighted code images directly from your R session — like [carbon.now.sh](https://carbon.now.sh) but without leaving R. It uses [Typst](https://typst.app) for rendering, so images are crisp at any size and fully themeable.

## Installation

Install the development version from [GitHub](https://github.com/christopherkenny/snippet):

``` r
pak::pak('christopherkenny/snippet')
```

`snippet` also requires [Typst](https://typst.app) to be installed on your system.

## Usage

Pass code as a string, a character vector, or a file path. Leave `code` empty to use your clipboard:

```{r example, eval = FALSE}
library(snippet)

snippet('fit <- lm(mpg ~ wt, data = mtcars)\nsummary(fit)')
```

### Themes

Two [Flexoki](https://stephango.com/flexoki) themes are bundled. List available themes with `snippet_themes()`:

```{r themes, eval = FALSE}
snippet(
  'fit <- lm(mpg ~ wt, data = mtcars)',
  theme = snippet_themes()[['Flexoki Dark']]
)
```

Install additional themes by name with `snippet_install_theme()`. See the full list with `snippet_known_themes()`:

```{r install-theme, eval = FALSE}
snippet_install_theme('Dracula')
snippet_install_theme('Tomorrow Night')

snippet('fit <- lm(mpg ~ wt, data = mtcars)', theme = snippet_themes()[['Dracula']])
```

You can also install any theme from a URL or local file path:

```{r install-theme-url, eval = FALSE}
snippet_install_theme('https://example.com/my-theme.tmTheme')
snippet_install_theme('/path/to/my-theme.tmTheme')
```

Or convert any VS Code JSON theme with `convert_theme()`:

```{r custom-theme, eval = FALSE}
convert_theme('path/to/my-vscode-theme.json')
```

### Window styles

```{r styles, eval = FALSE}
snippet('x <- 1', style = 'mac')      # macOS traffic lights
snippet('x <- 1', style = 'windows')  # Windows controls
snippet('x <- 1', style = 'none')     # no chrome
```

### Line numbers and width

```{r extras, eval = FALSE}
snippet(
  'x <- 1:10\nmean(x)\nsd(x)',
  line_numbers = TRUE,
  width = 4
)
```

### Copy to clipboard

Set `clip = TRUE` to copy the rendered PNG to your system clipboard immediately after rendering:

```{r clip, eval = FALSE}
snippet('x <- 1:10', clip = TRUE)
```
